---
title: "Gravimeter"
author: "Mike Longstreth's Workspace"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  flexdashboard::flex_dashboard:
    theme: cerulean
    orientation:: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(readr)
library(lubridate)
library(ggplot2)
library(tidyverse)
library(plotly)
# library(leaflet)
library(DT)
library(knitr)
library(scales)
```

```{r}
user_fee=c(100)
processing_cost=c(75)
promotion_cost=c(150)
hosting_cost=c(25)
budget=c(250000)
```

```{r}
users <- read_csv("users.csv")
users <- users %>%
  mutate(year_month = substr(mdy(users$access_date),0,7)) %>%
  select(attorney_name, year_month) %>%
  group_by(attorney_name, year_month) %>%
  summarize(access_count = n()) %>%
  mutate(monthly_user_fee = user_fee) %>%
  arrange(desc(year_month), attorney_name)

inv_users <- users %>%
  select(year_month, monthly_user_fee) %>%
  group_by(year_month) %>%
  summarize(sum(monthly_user_fee))
```

```{r}
edds <- read_csv("edds.csv")
edds <- edds %>%
  mutate(total_volume_GB = apply(edds[-1], 1, sum)) %>%
  mutate(cost_per_GB = hosting_cost) %>%
  mutate(monthly_hosting_cost = round((total_volume_GB * hosting_cost),2)) %>%
  arrange(desc(year_month))

inv_edds <- edds %>%
  select(year_month, monthly_hosting_cost)
```

```{r}
processing <- read_csv("processing.csv")
processing$date_submitted <- mdy(processing$date_submitted)
processing$date_complete <- mdy(processing$date_complete)
processing <- processing %>%
  mutate(year_month = substr(date_complete,0,7)) %>%
  mutate(cost_per_GB = processing_cost) %>%
  mutate(processing_cost = round((data_volume_post_exp_gb * processing_cost), 2)) %>%
  arrange(desc(year_month))

inv_processing <- processing %>%
  select(year_month, processing_cost) %>%
  group_by(year_month) %>%
  summarize(sum(processing_cost))
```

```{r}
promotion <- read_csv("promotion.csv")
promotion$date_submitted <- mdy(promotion$date_submitted)
promotion$date_complete <- mdy(promotion$date_complete)
promotion <- promotion %>%
  mutate(year_month = substr(date_complete,0,7)) %>%
  mutate(cost_per_GB = promotion_cost) %>%
  mutate(promotion_cost = round((total_of_natives_gb * promotion_cost), 2)) %>%
  arrange(desc(year_month))

inv_promotion <- promotion %>% 
  select(year_month, promotion_cost) %>%
  group_by(year_month) %>%
  summarize(sum(promotion_cost))
```

```{r}
invoices <- full_join(inv_processing, inv_promotion, by = 'year_month')

invoices <- full_join(invoices, inv_edds, by = 'year_month')

invoices <- full_join(invoices, inv_users, by = 'year_month')

invoices <- invoices %>%
  mutate(invoice_total = apply(invoices[-1], 1, sum, na.rm=TRUE)) %>%
  arrange(desc(year_month))

invoice_columns <- c('year_month', 'processing', 'promotion', 'hosting', 'users', 'total')

names(invoices) <- invoice_columns

inv_allocation <- gather(invoices, key='cost_type', value='amount', -year_month, -total) %>%
  select(cost_type, amount) %>%
  drop_na() %>%
  group_by(cost_type) %>%
  summarize(sum(amount))
inv_allocation_columns <- c('cost_type', 'amount')
names(inv_allocation) <- inv_allocation_columns

```

Overview
=====================================

Column {data-width=600}
---------------------

### Project Costs
```{r}
invoices_chart <- plot_ly(
  x = invoices$year_month,
  y = invoices$total,
  name = "Invoices",
  type = "bar") %>%
    layout(title = "Project Costs",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Cost"))

invoices_chart
```

***

> Average Invoice Cost: $`r toString(round(mean(invoices$total),2))`

### Invoices
```{r}
datatable(invoices,
          rownames = FALSE,
          extensions = 'Buttons', options = list(
            dom = 'Bfrtip',
            buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
          ))
```

Column {data-width=400}
---------------------

### Cost Allocation
```{r fig.height=7}
p <- plot_ly(
  x = inv_allocation$cost_type,
  y = inv_allocation$amount,
  name = "Cost Allocation",
  type = "bar",
  color = inv_allocation$cost_type
) %>%
  layout(title = "Cost Allocation",
         xaxis = list(title = "Tech Type"),
         yaxis = list(title = "Cost"),
         showlegend = FALSE)

p
```

### Unit Costs
```{r fig.height=3.5}
unit_costs <- data.frame("User" = dollar(user_fee),
                         "Processing" = dollar(processing_cost),
                         "Promotion" = dollar(promotion_cost),
                         "Hosting" = dollar(hosting_cost)
)
unit_costs <- gather(unit_costs, key='cost_type', value='amount')
unit_costs$unit <- c('Month', 'GB', 'GB', 'GB')

kable(unit_costs)
```

### Total Project Cost
```{r}
total_project_cost <- round(sum(invoices$total),2)

valueBox(dollar(total_project_cost), 
         icon = "fa-money-bill-wave",
         color = "info")
```

### Current Budget
```{r}
valueBox(dollar(budget), 
         icon = "fa-wallet",
         color = "success")
```

### Percent of Budget Used
```{r}
project_status <- round((total_project_cost / budget) * 100)

gauge(value = project_status,
      min = 0,
      max = 100,
      symbol = '%',
      sectors = gaugeSectors(success = c(0, 66),
                             warning = c(67, 90),
                             danger = c(91, 100)))

```


Tech Charges {data-orientation=rows}
=====================================

Row {data-height=500 .tabset .tabset-fade}
---------------------

### Processing Overview
```{r}
processing_overivew <- plot_ly(
  x = processing$year_month,
  y = processing$processing_cost,
  name = "Processing Overview",
  type = "bar") %>%
    layout(title = "Processing Costs",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Cost"))

processing_overivew
```

***

> Total Processing Costs: $`r toString(round(sum(processing$processing_cost),2))`;
> Total GB Processed: `r toString(round(sum(processing$data_volume_post_exp_gb),2))`

### Processing Details
```{r}
datatable(processing,
          rownames = FALSE,
          extensions = 'Buttons', options = list(
            dom = 'Bfrtip',
            buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
          ))
```

***

> Total Processing Costs: $`r toString(round(sum(processing$processing_cost),2))`;
> Total GB Processed: `r toString(round(sum(processing$data_volume_post_exp_gb),2))`

Row {data-height=500 .tabset .tabset-fade}
---------------------

### Promotion Overview

```{r}
promotion_overivew <- plot_ly(
  x = promotion$year_month,
  y = promotion$promotion_cost,
  name = "Processing Overview",
  type = "bar") %>%
    layout(title = "Promotion Costs",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Cost"))

promotion_overivew
```

***

> Total Promotion Costs: $`r toString(round(sum(promotion$promotion_cost),2))`;
> Total GB Promoted: `r toString(round(sum(promotion$total_of_natives_gb),2))`

### Promotion Details
```{r}
datatable(promotion,
          rownames = FALSE,
          extensions = 'Buttons', options = list(
            dom = 'Bfrtip',
            buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
          ))
```


***

> Total Promotion Costs: $`r toString(round(sum(promotion$promotion_cost),2))`;
> Total GB Promoted: `r toString(round(sum(promotion$total_of_natives_gb),2))`


Monthly Charges
=====================================

Column {data-width=500}
---------------------

### Hosting Details
```{r}
datatable(edds,
          rownames = FALSE,
          extensions = 'Buttons', options = list(
            dom = 'Bfrtip',
            buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
          ))
```

> Total Hosting Costs: $`r toString(round(sum(edds$monthly_hosting_cost),2))`

### Hosting Overview
```{r}
hosting_overivew <- plot_ly(
  x = edds$year_month,
  y = edds$monthly_hosting_cost,
  name = "Hosting Overview",
  type = "bar") %>%
    layout(title = "Hosting Costs",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Cost"))

hosting_overivew
```


Column {data-width=500}
---------------------

### Users Details
```{r}
datatable(users,
          rownames = FALSE,
          extensions = 'Buttons', options = list(
            dom = 'Bfrtip',
            buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
          ))
```

> Total User Fees: $`r toString(round(sum(users$monthly_user_fee),2))`

### Users Overview
```{r}
inv_users <- plot_ly(
  x = inv_users$year_month,
  y = inv_users$`sum(monthly_user_fee)`,
  name = "Users Overview",
  type = "bar") %>%
    layout(title = "User Costs",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Cost"))

inv_users
```